Fast, Scalable Phrase-Based SMT Decoding

### 2016-02-04 acl.2016/acl2016.tex
acl paper

Over 24\% of the Moses decoder running time is spent on memory management and this increases when more threads are used, Table~\ref{tab:optimizing-memory}, dampening the scalability ofthe decoder. By contrast, our decoder spends 11\% on memory management and does not significantly increase with more cores.
\begin{table}[h]
\begin{center}
\small
\begin{tabular}{|l|c|c|c|c|} \hline
		& \multicolumn{2}{c|} {Moses}	& \multicolumn{2}{c|} {Our Work} \\ \hline
\# threads	& 1 		& 32	& 1 		& 32  \\ \hline
Memory  	& 24\%		& 39\% 	& 11\%		& 13\% \\
LM 		& 12\%	 	& 2\% 	& 47\%		& 38\% \\ 
Phrase-table	& 9\%	 	& 5\% 	& 2\%		& 4\% \\ 
Lex RO 		& 8\%	 	& 2\% 	& 2\%		& 2\% \\ 
Search 		& 2\%	 	& 0\% 	& 14\%		& 19\% \\ 
Misc/Unknown	& 45\%	 	& 39\% 	& 24\%		& 29\% \\ \hline
\end{tabular}
\end{center}
\caption{Profile of \%age decoding time}
\label{tab:optimizing-memory}
\end{table}

@@

The cube-pruning algorithm contain a further priority queue which is attached to hypotheses sets which can be independent of how hypotheses are grouped. In the Moses implementation, the priority queue is also attached to the coverage cardinality, Figure~\ref{algo:Cube Pruning with Unsorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\STATE initialize $queue_{|C|}$
\FOR{1 to pop-limit}
  \STATE get best $item$ in $queue_{|C|}$
  \STATE create new hypo from $item$
  \STATE add new hypo to new $stack_{|C|}$
  \STATE create next $items$
  \STATE add new $items$ to $queue_{|C|}$
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Cube Pruning with Unsorted Stack}
\label{algo:Cube Pruning with Unsorted Stack}
\end{figure}
Again, we experiment with diffirent queue configurations, having separate queues for each cardinality, coverage, and coverage \& end position. The stack configuration remained constant (coverage \& end position with pop-limit of 400).
\begin{table}[h]
\small
\begin{center}
\begin{tabular}{|r|r|r|} \hline
Queue configuration		& Time		& Score \\ \hline
Cardinality			& 192		& -8.59922 \\
Coverage			&		& -8.58635 \\
Coverage \& end position	&		& -8.58263 \\ \hline
\end{tabular}
\end{center}
\caption{Decoding time (in secs with 32 threads) and average model scores for different queue configurations}
\label{tab:queue-configuration}
\end{table}
From the results in Table~\ref{tab:queue-configuration}, using finer grain queues results in better model scores, it is significantly slower to decode.

>>>>

Over 24\% of the Moses decoder running time is spent on memory management and this increases when more threads are used, Table~\ref{tab:optimizing-memory}, dampening the scalability of the decoder. By contrast, our decoder spends 11\% on memory management and does not significantly increase with more cores.
\begin{table}[h]
\begin{center}
\small
\begin{tabular}{|l|c|c|c|c|} \hline
		& \multicolumn{2}{c|} {Moses}	& \multicolumn{2}{c|} {Our Work} \\ \hline
\# threads	& 1 		& 32	& 1 		& 32  \\ \hline
Memory  	& 24\%		& 39\% 	& 11\%		& 13\% \\
LM 		& 12\%	 	& 2\% 	& 47\%		& 38\% \\ 
Phrase-table	& 9\%	 	& 5\% 	& 2\%		& 4\% \\ 
Lex RO 		& 8\%	 	& 2\% 	& 2\%		& 2\% \\ 
Search 		& 2\%	 	& 0\% 	& 14\%		& 19\% \\ 
Misc/Unknown	& 45\%	 	& 39\% 	& 24\%		& 29\% \\ \hline
\end{tabular}
\end{center}
\caption{Profile of \%age decoding time}
\label{tab:optimizing-memory}
\end{table}

@@

The cube-pruning algorithm contain a further priority queue which is attached to hypotheses sets which can be independent of how hypotheses are grouped. In the Moses implementation, the priority queue is also attached to the coverage cardinality, Figure~\ref{algo:Cube Pruning with Unsorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\STATE initialize $queue_{|C|}$
\FOR{1 to pop-limit}
  \STATE get best $item$ in $queue_{|C|}$
  \STATE create new hypo from $item$
  \STATE add new hypo to new $stack_{|C|}$
  \STATE create next $items$
  \STATE add new $items$ to $queue_{|C|}$
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Cube Pruning with Unsorted Stack}
\label{algo:Cube Pruning with Unsorted Stack}
\end{figure}
Again, we experiment with diffirent queue configurations, having separate queues for each cardinality, coverage, and coverage \& end position. The stack configuration remained constant (coverage \& end position with pop-limit of 400).
\begin{table}[h]
\small
\begin{center}
\begin{tabular}{|r|r|r|} \hline
Queue configuration		& Time		& Score \\ \hline
Cardinality			& 192		& -8.59922 \\
Coverage			& 2413		& -8.58635 \\
Coverage \& end position	& 7472		& -8.58263 \\ \hline
\end{tabular}
\end{center}
\caption{Decoding time (in secs with 32 threads) and average model scores for different queue configurations}
\label{tab:queue-configuration}
\end{table}
From the results in Table~\ref{tab:queue-configuration}, using finer grain queues results in better model scores but it is significantly slower to decode.
